% basic part begin
\documentclass[10pt, a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[misc]{ifsym}
\usepackage{makeidx}
\usepackage{wasysym}
\usepackage{enumitem}
% basic part end

\usepackage{multicol}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage[left=1cm,right=1cm,top=1cm,bottom=1cm]{geometry}

\author{Balakhnin Sergei}

\setlength\columnsep{15mm}
\setlength\parindent{0pt}
\pagenumbering{gobble}

\begin{document}

    \section*{Balakhnin Sergei}

    {\large\textbf{Software Engineer}}

    \hbox{\large\textbf{Contacts}}\kern5pt\hrule\kern5pt

    \faPhone: +7-952-265-18-42

    \Letter: serg17alb@gmail.com

    \faGithub: \url{http://www.github.com/sergalb}

    \faSend: \url{http://www.t.me/serg_alb}

    \faLinkedinSquare: \url{https://www.linkedin.com/in/sergey-balakhnin-790180228/}\\




    \par\hbox{\large\textbf{Work Experience}}\kern3pt\hrule\kern10pt

    JetBrains, Qodana team. \\
    Stack: Kotlin, Java, Static Analysis \\
    Specialization: developer in core team of static analyzer tool.\\
    \underline{Period: 7.2021 - 03.2022} \\

    Huawei, Programming Language team. \\
    Stack: C/C++, research \\
    Specialization: develop translator from Java to other language \\
    \underline{Period: 10.2020 - 04.2021} \\

    Huawei, project - LLVM compiler. \\
    Stack: C/C++, research \\
    Specialization: develop profile guided optimization for clang compiler\\
    \underline{Period: 06.2020 - 10.2020} \\

    Tinkoff internship, project - website kassir.ru. \\
    Stack: Java, Kotlin, Spring \\
    Specialization: Backend-developer \\
    \underline{Period: 06.2019 - 09.2019} \\

 \par\hbox{\large\textbf{Education}}\kern5pt\hrule\kern5pt

    \textbf{Bachelor's degree at Computer Science in ITMO.}
    \hfill
    \textbf{ GPA: 4.1 / 5} \\
        Specialisation: mathematics and Computer Science. ITMO is 79-th world university by CS based on "QS World University Ranking".\\


    \par\hbox{\large\textbf{Key skills}}\kern5pt\hrule\kern5pt

    \begin{itemize}

        \item \textbf{Programming languages.}

        Industry Experience: Kotlin, Java. Educational knowledge: Haskell, Go, C++, Python.

        \item Deep knowledges of algorithm and data structure.
        \item Theoretical and practical experience in multiprocessing programming.
        \item SQL.
        \item Professional English.
        \item Git experience.
        \\
    \end{itemize}

    \par\hbox{\large\textbf{Educational projects, achievements}}\kern5pt\hrule\kern5pt
    \begin{itemize}

        \item \textbf{Bachelor's thesis}. Work on active module identification problem in bioniformatics domain. Upgrade approach discribed in: \href{https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03572-9}{\textit{Markov chain Monte Carlo for active module identification problem}}\\
        My solution add support for another kind of input data (add support for metabolics networks).\\
        Stack: R, C++
        Project link:
        \textbf{
        \url{https://github.com/sergalb/mcmcRanking}
        }


        \item \textbf{LALR-grammar parser's generator} (subset ANTLR)\\
        Stack: Kotlin, ANTLR\\
        Project link:
        \textbf{
        \url{https://github.com/sergalb/ParserGenerator}
        }

        \item \textbf{Utility for searching substring in directory} (analogy to grep, with UI)\\
        Stack: C++, QtCreator, Multithreading.\\
        In this project, I managed to achieve a performance that exceeds grep (due to pre-calculation)\\
        Project link:
        \textbf{
        \url{https://github.com/sergalb/cpp-third-term/tree/master/SubstringFinder}
        }

        \item \textbf{Android apps}\\
        Stack: Kotlin, Multithreading, REST\\
        Project link:
        \textbf{
        \url{https://github.com/sergalb/android-2019}
        }

        \item \textbf{Haskell applications}\\
        Stack: Haskell, ghc \\
        hw-2: Own file-system and base version system\\
        hw-3: Atomic tasks on lenses, concurency, interpretor of JavaScript subset\\
        \textbf{
        \url{https://github.com/sergalb/fp}
        }

        \item \textbf{Factorizing big numbers with dixon's method}\\
        Stack: Kotlin, mapple, linear algebra\\
        implementation of \href{https://en.wikipedia.org/wiki/Dixon\%27s_factorization_method}{\textit{Dixon}}
        \textbf{
        \url{https://github.com/sergalb/computer-algebra}
        }

        \item Prize-winning in math olympiads - "Rosatom", "PhysTech", "OMMO", "Future researchers - the future of science"
        \item 3 years volunteering on NERC ICPC final (semi-final of whole world programming competition)
    \end{itemize}

\end{document}